---
title: "Case Study 1"
author: "Allen Ansari,Audrene Tiakor"
date: "February 17, 2019"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
setwd("C:\\Users\\Audrene\\Desktop\\Beer_Study-master")
```


```{r message=FALSE, warning=FALSE, , include=TRUE, paged.print=FALSE}
library(ggplot2) # Data visualization
library(readr) # CSV file I/O, e.g. the read_csv function
library(dplyr) # Heavy use of this library
library(tidyr)
library(plyr)
library(ggthemes) # for themes in ggplot
library(knitr)
library(kableExtra) # library to make the document more presentable
library(Amelia) # for missing map
```

```{r}
# Read in beer and breweries data set using _csv for more tidy output
Beers <- read_csv('Beers.csv', col_types = cols())
Breweries <- read_csv('Breweries.csv', col_types = cols())
```

### 1. How many breweries are present in each state?

To answer this question we used table function to  retrieve the value of `State` from the `Breweries` data.
```{r}
BrewPerState <-table(Breweries$State)
BrewPerState

```
### 2. Merge beer data with the breweries data. Print the first 6 observations and the last six observations to check the merged file.
We can merge them into a single dataset, using `full_join` unisng Brewery_id from Beers dataset and Brew_ID from Breweries dataset.
```{r}
BrewPub <- merge(Beers, Breweries, by.x = "Brewery_id", by.y = "Brew_ID", all = TRUE)
# Change variable names to more meaningful title

BrewPub <- rename(BrewPub, c("Name.x"="Beer","Name.y"="Brewery",
                   "Ounces"="OZ"))
# Used kable library to make document more presentable
kable(BrewPub %>% 
         head()) %>%
         kable_styling("striped", full_width = F)
        

kable(BrewPub %>% 
         tail()) %>%
         kable_styling("striped", full_width = F) 
         

```

### 3. Report the number of NA's in each column.


To do this, we use a function (which returns `true` if a given value is NA, `false` otherwise, using `is.na`) and `sapply` to determine the number of missing values for each column within `BrewPub`.

Per the results, we find that there are a total of 62 ABV values missing, 1005 IBU values amd 5 Style values missing. No other data is missing.
```{r}
MissingValues <- sapply(BrewPub, function(MissingValue)sum(is.na(MissingValue)))

# Used kable library to make document more presentable
as.data.frame(MissingValues) %>%
  kable("html") %>%
  kable_styling("striped", full_width = F) 

missmap(BrewPub,y.at=c(1),y.labels = c(''),col=c('yellow','black'))
  

```

### 4. Compute the median alcohol content and international bitterness unit for each state. Plot a bar chart to compare.

```{r}
# 4. Compute the median alcohol content unit for each state.
Alc <- BrewPub %>%
  na.omit()  %>%
group_by(State) %>%
summarise_each(funs(median), Median_ABV = ABV) %>%
arrange(Median_ABV)
Alc
```

```{r}
# 4. a Compute the median international bitterness unit for each state.
Bitter <- BrewPub %>%
  na.omit() %>%
group_by(State) %>%
summarise_each(funs(median), Median_IBU = IBU) %>%
arrange(Median_IBU)
Bitter
```

```{r}
# 4. b Plot a bar chart to compare ABV by state

ggplot(data=Alc, aes(x=State, y=sort(Median_ABV,decreasing = TRUE))) +
  geom_bar(stat="identity", fill="red")+
  theme_bw() + 
  scale_color_economist()+
  theme(axis.text.x=element_text(size=rel(0.8), angle=90),plot.title = element_text(size=14,hjust = 0.5, face="bold.italic")) +
  ggtitle("Median ABV by State") +
  labs(x="State",y="ABV")

```


```{r}
# 4. c Plot a bar chart to compare IBU by state
ggplot(data=Bitter, aes(x=State, y=Median_IBU)) +
  geom_bar(stat="identity", fill="steelblue")+
  theme_bw() + 
  scale_color_economist()+
  theme(axis.text.x=element_text(size=7, angle=90),plot.title = element_text(size=14,hjust = 0.5, face="bold.italic"))+ ggtitle("Median IBU by State") + labs(x="State",y="IBU")

```

## 5- Which state has the maximum alcoholic (ABV) beer? Which state has the most bitter (IBU) beer?

``` {r}
# finding state which has has the maximum alcoholic (ABV) beer
Max_ABV <- Alc[which.max(Alc$Median_ABV),]
Max_ABV
# finding state which has has the maximum alcoholic (IBU) beer
Max_IBU <- Bitter[which.max(Bitter$Median_IBU),]
Max_IBU
``` 
## 6- Summary statistics for the ABV variable
To do this, we apply the function summary() to the variable ABV (alcohol content of our data set 'BrewPub'), which returns descriptive statistics of ABV such as the minimum value (smallest value of ABV), the first quartile, the median, the mean, the thrid quartile, and the maximum (largest value of ABV).
``` {r}
# summary statistics for the ABV variable
summary(BrewPub$ABV)
``` 

## 7- Is there an apparent relationship between the bitterness of the beer and its alcoholic content?
``` {r}
# drawing a Scatter plot Bitterness of Beer vs Alcholic content
ggplot(BrewPub, aes(x=BrewPub$IBU, y=BrewPub$ABV)) + geom_point() + geom_smooth(method=lm, se=FALSE) + theme(plot.title = element_text(size=14,hjust= 0.5, face="bold.italic")) + ggtitle("Relationship Between Bitterness of Beer and Its Alcoholic Content") +
  labs(x="Bitterness",y="Alcoholic Content") 

``` 
After plotting a scatter plot to depict the relationship between the bitterness of the beer and its alcoholic content, we can see that there is a positive correlation between the bitterness of the beer and its alcoholic content. The higher the alcohol content, the more bitter the beer will taste. 

## EDA##
``` {r}
Alch<-ggplot((BrewPub), aes(x = BrewPub$State, y = BrewPub$ABV)) + geom_boxplot() + theme(axis.text.x=element_text(size=7, angle=90), plot.title = element_text(size=14,hjust = 0.5, face="bold.italic"))+ ggtitle("Boxplot of Alcohol Content By State") + labs(x="State",y="AVC")

Bitt<- ggplot((BrewPub), aes(x = BrewPub$State, y = BrewPub$IBU)) + geom_boxplot() + theme(axis.text.x=element_text(size=7, angle=90), plot.title = element_text(size=14,hjust = 0.5, face="bold.italic"))+ ggtitle("Boxplot of Beer Bitterness By State") + labs(x="State",y="IBU")
``` 